Pilot study APEROL: questionnaire data

### 2021-01-22 paper_1/paper_1_supplement.Rmd
paper supplement

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf # hier kann man auch word irgendwie machen
---

@@

Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.

(ref:thisisdialectical-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.

```{r dialectical, fig.cap = "(ref:thisisdialectical-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/thisisdialectical.png", dpi = 108)

@@

```{r demographicspilot1table,echo=FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)

@@

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
            )

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

## Procedure

@@

### Questionnaire Data
*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

@@

```{r demographicspilot1table,,echo=FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

@@

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "Male" = sum(gender),
            "M age" = round(mean(age), 2),
            "Min age" = min(age),
            "Max age" = max(age),
            "SD age" = round(sd(age), 2),
            "M exp." = round(mean(experience), 2),
            "Min exp." = min(experience),
            "Max exp." = max(experience),
            "SD exp." = round(sd(experience), 2),
           )

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Informationand and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

## Data collection

(ref:data_collection-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.

```{r data collection, fig.cap = "(ref:data_collection-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/data_collection.png", dpi = 108)

@@

### Questionnaire Data
*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.*

The questionnaire contains the following scales:

(1) classroom management
(2) positive climate and motivation
(3) clarity and structuredness
(4) activation and support
(5) presence: posture and gaze
(6) presence: voice
(7) presence: verbal and non-verbal intervention
(8) turn taking
(9) natural behaviour

The table below provides an overview over the mean, min, max and standard deviation of all scales.

```{r table all sclaes, echo=FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create a basic table (tibble) using tidyverse functions 
scale.quest.table <- quest.raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2),
            )

# format and insert table in manuscript
apa_table(
  scale.quest.table,
  caption = "Mean values of all scales",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

### 2021-01-22 paper_1/paper_1_supplement.tex
paper supplement

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher},
  pdfauthor={Mandy Klatt1 \& Gregor Kachel1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events. This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017). Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff et al., 2017)

Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff et al., 2017). For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students. The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017). Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010). Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).

Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.

\begin{figure}

{\centering \includegraphics{./pictures/thisisdialectical}

\caption{Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.}\label{fig:dialectical}
\end{figure}

@@

\caption{\label{tab:demographicspilot1table,}Demographic Information}

@@

\begin{tabular}{lllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{mean age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
\bottomrule
\end{tabular}

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

@@

The lesson disturbances were displayed as instructions during the lesson for all \enquote{students} but not the teacher. In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase. In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.

@@

\emph{Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.} Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

@@

We used R (Version 4.0.2; R Core Team, 2019) and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{papayar} (Muschelli, 2016), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.5; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019) for all our analyses.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

@@

\leavevmode\hypertarget{ref-cortina2015low}{}%
Cortina, K. S., Miller, K. F., McKenzie, R., \& Epstein, A. (2015). Where low and high inference data converge: Validation of class assessment of mathematics instruction using mobile eye tracking with expert and novice teachers. \emph{International Journal of Science and Mathematics Education}, \emph{13}(2), 389--403.

@@

\leavevmode\hypertarget{ref-messner2000berufliche}{}%
Messner, H., \& Reusser, K. (2000). Die berufliche entwicklung von lehrpersonen als lebenslanger prozess. \emph{Beiträge Zur Lehrerinnen-Und Lehrerbildung}, \emph{18}(2), 157--171.

\leavevmode\hypertarget{ref-R-papayar}{}%
Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya javascript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}

@@

\leavevmode\hypertarget{ref-stuermer2017eye}{}%
Stuermer, K., Seidel, T., Mueller, K., Häusler, J., \& Cortina, K. S. (2017). What is in the eye of preservice teachers while instructing? An eye-tracking study about attention processes in different teaching situations. \emph{Zeitschrift Für Erziehungswissenschaft}, \emph{20}(1), 75--92.

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

@@

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., \ldots{} Yutani, H. (2019). Welcome to the tidyverse. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher},
  pdfauthor={Mandy Klatt1 \& Gregor Kachel1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events. This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017). Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff, Jarodzka, \& Boshuizen, 2017)

Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff, Jarodzka, \& Boshuizen, 2017). For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students. The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017). Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010). Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).

@@

\caption{\label{tab:demographicspilot1table,}Demographic Informationand and Teaching Experience}

@@

\begin{tabular}{lllllllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M age} & \multicolumn{1}{c}{Min age} & \multicolumn{1}{c}{Max age} & \multicolumn{1}{c}{SD age} & \multicolumn{1}{c}{M exp.} & \multicolumn{1}{c}{Min exp.} & \multicolumn{1}{c}{Max exp.} & \multicolumn{1}{c}{SD exp.}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95 & 20.00 & 15.00 & 25.00 & 7.07\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89 & 0.68 & 0.00 & 1.50 & 0.68\\
\bottomrule
\end{tabular}

@@

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

(ref:data\_collection-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.

\textbackslash begin\{figure\}

\{\centering \includegraphics{./pictures/data_collection}

\}

\textbackslash caption\{(ref:data\_collection-caption)\}(\#fig:data collection)
\textbackslash end\{figure\}

@@

The lesson disturbances were displayed as instructions during the lesson for all ``students'' but not the teacher. In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase. In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.

@@

\emph{Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.}

The questionnaire contains the following scales:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  classroom management
\item
  positive climate and motivation
\item
  clarity and structuredness
\item
  activation and support
\item
  presence: posture and gaze
\item
  presence: voice
\item
  presence: verbal and non-verbal intervention
\item
  turn taking
\item
  natural behaviour
\end{enumerate}

The table below provides an overview over the mean, min, max and standard deviation of all scales.

\begin{verbatim}
## Warning: Problem with `mutate()` input `value`.
## i NAs durch Umwandlung erzeugt
## i Input `value` is `as.numeric(as.character(factor(value)))`.
\end{verbatim}

\begin{verbatim}
## Warning in mask$eval_all_mutate(dots[[i]]): NAs durch Umwandlung erzeugt
\end{verbatim}

\caption{\label{tab:table all sclaes}Mean values of all scales}

\begin{tabular}{llllll}
\toprule
group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
\midrule
expert & Aktivierung und Förderung & 2.82 & 1.00 & 4.00 & 1.11\\
expert & Klarheit und Strukturiertheit & 3.46 & 1.00 & 4.00 & 0.89\\
expert & Klassenmanagement & 3.36 & 1.00 & 4.00 & 0.80\\
expert & Lernförderliches Klima und Motivierung & 3.60 & 2.00 & 4.00 & 0.62\\
expert & Manipulationsitem & 3.55 & 2.00 & 4.00 & 0.69\\
expert & Manipulationsitem & 3.60 & 3.00 & 4.00 & 0.52\\
expert & Präsenz/Haltung\_Blick & 3.29 & 1.00 & 4.00 & 0.92\\
expert & Präsenz/Stimme & 2.70 & 1.00 & 4.00 & 1.16\\
expert & Präsenz/Stimme\ \ & 3.57 & 2.00 & 4.00 & 0.63\\
expert & Präsenz/verbale\_nonberbale Intervention & 3.07 & 2.00 & 4.00 & 0.78\\
expert & Redeanteil & 74.20 & 60.00 & 95.00 & 10.53\\
novice & Aktivierung und Förderung & NA & NA & NA & NA\\
novice & Klarheit und Strukturiertheit & 3.21 & 1.00 & 4.00 & 0.87\\
novice & Klassenmanagement & 2.85 & 0.00 & 4.00 & 0.91\\
novice & Lernförderliches Klima und Motivierung & 3.11 & 0.00 & 4.00 & 0.90\\
novice & Manipulationsitem & 2.90 & 2.00 & 4.00 & 0.45\\
novice & Manipulationsitem & 3.20 & 2.00 & 4.00 & 0.75\\
novice & Nachdenkzeit & NA & NA & NA & NA\\
novice & Präsenz/Haltung\_Blick & 2.95 & 0.00 & 4.00 & 0.95\\
novice & Präsenz/Stimme & 3.19 & 0.00 & 4.00 & 1.04\\
novice & Präsenz/Stimme\ \ & 3.07 & 2.00 & 4.00 & 0.69\\
novice & Präsenz/verbale\_nonberbale Intervention & 2.95 & 1.00 & 4.00 & 0.91\\
novice & Redeanteil & 76.93 & 50.00 & 95.00 & 12.97\\
novice & Störung & NA & NA & NA & NA\\
\bottomrule
\end{tabular}

@@

We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al. (2019){]} for all our analyses.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

@@

\leavevmode\hypertarget{ref-cortina2015low}{}%
Cortina, K. S., Miller, K. F., McKenzie, R., \& Epstein, A. (2015). Where low and high inference data converge: Validation of CLASS assessment of mathematics instruction using mobile eye tracking with expert and novice teachers. \emph{International Journal of Science and Mathematics Education}, \emph{13}(2), 389--403.

@@

\leavevmode\hypertarget{ref-messner2000berufliche}{}%
Messner, H., \& Reusser, K. (2000). Die berufliche entwicklung von lehrpersonen als lebenslanger prozess. \emph{Beitr{ä}ge Zur Lehrerinnen-Und Lehrerbildung}, \emph{18}(2), 157--171.

\leavevmode\hypertarget{ref-R-papayar}{}%
Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya JavaScript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}

@@

\leavevmode\hypertarget{ref-stuermer2017eye}{}%
Stuermer, K., Seidel, T., Mueller, K., Häusler, J., \& Cortina, K. S. (2017). What is in the eye of preservice teachers while instructing? An eye-tracking study about attention processes in different teaching situations. \emph{Zeitschrift f{ü}r Erziehungswissenschaft}, \emph{20}(1), 75--92.

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

@@

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

@@

\end{CSLReferences}

### 2021-01-22 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
paper supplement

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)

@@

# demographics, grouped by group (N, gender, meanage, max, min age)
raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "experience" = round(mean(experience), 2)
            ) %>% 
  knitr::kable(digits = 2)

@@

```{r mean classroom management, echo = FALSE}

### classroom management

# filter by parameter variable, i.e. create a subset for each session
km.data <- raw.data %>% filter(scale == "Klassenmanagement")

view (km.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create  mean, min, max, sd of classroom management
km.data.plot %>% km.data %>%

          meankm <- mean(km.data$value)
          minkm <- min(km.data$value)
          maxkm <- max(km.data$value)
          sdkm <- sd(km.data$value)
          Nkm <- km.data %>% summarise(N = n_distinct(personID))
          mdkm <- median(km.data$value)

@@

### to do

- vergessen: Berufserfahrung bei Demographie mit aufnehmen
- selbst und fremdeinschätzung durch facet_grid bei plot hinzufügen

>>>>

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
# import: never forget to insert "dec="," for replacing values with "," by "."
raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

@@

# years of experience
class(raw.data$experience)

# converting numbers to numeric
raw.data <- raw.data %>%  mutate(experience = as.numeric(as.character(factor(experience))))

# demographics and years of experience, grouped by group (N, gender, M age, max, min age)
raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "SD age" = round(sd(age), 2),
            "M experience" = round(mean(experience), 2),
            "min experience" = min(experience),
            "max experience" = max(experience),
            "SD experience" = round(sd(experience), 2),
            ) %>% 
  knitr::kable(digits = 2)

@@

```{r table all sclaes, echo=FALSE}

sum(is.na(raw.data$scale == "Aktivierung und Förderung"))

# value sometimes contained text before filtering, we have to convert the numbers to numeric
raw.data <- raw.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create a table of all scales 
raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2),
            ) %>% 
  knitr::kable(digits = 2)

@@
